---
title: "Mapping"
author: "Barry DeCicco"
date: "4/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mapping in R

'Mapping' here means any of a number of methods to take a problem, break it into parts, apply some command/function to the parts, and then reassembling the results back into a unified object.

#### Reading CSV files, Method 1: 

 This is from:  https://riptutorial.com/r/example/24397/import-multiple-csv-files
 
- The first step is to set the working directory to the 'data' folder, and to store the old working directory.

- The second step is to create a list of the files in that working directory.

- The third step is to use the lapply command to that list, using the read.csv function, creating a 'data_list' wich is a list of data frames.

- The fourth step is to combine the elements of that list into a single data frame, by stacking them (rbind stacks row vertically, cbind attaches columns horizontally).

```{r method1, include=TRUE}


oldwd <- setwd('Data')
files = list.files(pattern="*.csv")
files
data_list = lapply(files, read.csv)
data_list

df <- do.call(rbind, data_list)
```

Information on the lapply function can be found at:  https://www.guru99.com/r-apply-sapply-tapply.html


## Method 2:  Using the 'plyr' package

From:  https://datascienceplus.com/how-to-import-multiple-csv-files-simultaneously-in-r-and-create-a-data-frame/

Plyr instructions are found at:  https://cran.r-project.org/web/packages/plyr/index.html


- Load the packages (install if needed).
- set up a file list 'myfiles'.
- Set the directory to 'Data'.
- use the ldply to go through the 'myfiles' list of files, applying the 'read_csv' function.

```{r pressure, echo=TRUE}
library(plyr)
library(readr)  # from the tidyverse

myfiles = list.files(path=mydir, pattern="*.csv", full.names=TRUE)
myfiles

mydir = "Data"

dat_csv = ldply(myfiles, read_csv)
dat_csv
```

